---
title: "Lab 7- Multiple Linear Regression"
author: "German Silva"
date: "11/8/2021"
output: html_document
---

```{r setup, warning = FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

# Attach packages
library(tidyverse)
library(palmerpenguins)
library(GGally)
library(broom)
library(kableExtra)
library(modelsummary)
```

## Intro to ggpairs

Use `GGally::ggpairs()` function to create a pairs plot

```{r}
ggpairs(penguins)
```

```{r}
penguins %>% 
  select(species, bill_length_mm:body_mass_g) %>% 
  ggpairs(aes(color = species))

ggplot(penguins, aes(x=bill_depth_mm, y = body_mass_g, group = species))+
  geom_point(aes(color = species)) +
  geom_smooth(method = "lm")
```

## Multiple Linear Regression Penguins

Use multiple linear regression to try to understand the relationship between mutliple predictor variables and a single continuous outcome variable (body mass).

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm + bill_depth_mm, data = penguins)

# return just the coefficients
penguin_lm
```

How would you interpret this coefficient for flipper_length_mm?

On average, we expect a 1 mm increase in flipper length to be associated with a 51.44g increase in body mass if everything else is held constant. 

use `summary()` function to get more information

```{r}
summary(penguin_lm)
```

R^2 means that 76% of the variance in body_mass_g that is explained by the model

### Use `broom` functions tidy and glance

Use `broom::tidy()` to getthe coefficient summary in a data frame
use `broom::glance()` ro get the model summary in a data frame

```{r}
penguin_lm_tidy <- tidy(penguin_lm)

penguin_lm_tidy
```

Try to use in-line code to refer to the bill depth coefficient. 

`r penguin_lm_tidy$estimate[3]`


```{r}
penguin_lm_glance <- glance(penguin_lm)

penguin_lm_glance
```

## Try another model

We have thought really hard, done a lit review, consulted with experts, deeply explored our data, and decided that the three most critical variables to include in the model are:

- flipper length
- species
- sex

Task: create a multivariate linear regression model using those 3 predictors variables

Then take a look at the model outputs and interpret the coefficients with a neighbor

```{r}
penguin_lm_2 <- lm(body_mass_g ~ flipper_length_mm + species + sex, data = penguins)

penguin_lm_2

penguin_lm_2_tidy <- tidy(penguin_lm_2)

penguin_lm_2_tidy
```

mass(g) = `r penguin_lm_2_tidy$estimate[1]`+ `r penguin_lm_2_tidy$estimate[2]` * flipper length (mm) + `r penguin_lm_2_tidy$estimate[3]` * Chinstrap + `r penguin_lm_2_tidy$estimate[4]` * Gentoo + `r penguin_lm_2_tidy$estimate[5]` * Male






